---
title: "Parameters"
title-slide-attributes: 
  data-background-color: "#43464B"
subtitle: "Session - running reports from different inputs"
author: "Zoë Turner"
format:
  revealjs:
    theme: [default, nhsr-quarto.scss]
    logo: https://raw.githubusercontent.com/nhs-r-community/assets/main/logo/nhsr-logo.svg
    code-link: true
    css: nhsr-quarto.scss
    self-contained: true
    preview-links: true
execute: 
  echo: fenced
  eval: false
embed-resources: true  
---

```{r}
#| label: packages
#| eval: true
#| echo: false
#| include: false
library(quarto)

```

## Using {quarto}

```{r}
quarto::quarto_render("my_report.qmd", 
                      execute_params = list(country = "United_Kingdom"),
                      output_format = "html"
)
 
```

## More than one parameter

```{r}
quarto::quarto_render("my_report.qmd", 
                      execute_params = list(country = "United_Kingdom",
                                            month_start = "2020-01-01",
                                            month_end = "2020-01-01"),
                      output_format = "html"
)
 
```

## Rendering multiple reports

The parameters have been for just one report but if we need to run several in one go we need to a function and a loop in R.

::: {.incremental}
- A function - is a block of code which only runs when its called (Source: [W3Schools](https://www.w3schools.com/r/r_functions.asp))
- A loop - is used for repeating code and can be used with functions
:::

## A function

Starts with a name: `run_docs`

```{r}
run_docs <- function() {
  }
```

. . .

Takes inputs (called parameters/arguments)

```{r}
run_docs <- function(country, month_start) {

  }

```

. . .

Call the {quarto} package which we've used before

```{r}
run_docs <- function(country, month_start) {
  quarto::quarto_render(
    "my_report.qmd",
    output_format = "html",
    execute_params = list(country = country, 
                          month_start = month_start)
  )
  }
```

## Naming the files

In this function we can also use the parameters to create distinct file names

```{r}
#| code-line-numbers: 9
run_docs <- function(country, month_start) {
  quarto::quarto_render(
    "my_report.qmd",
    output_format = "html",
    execute_params = list(country = country, 
                          month_start = month_start),
    output_file = glue::glue("{country} {month}.html") # creates the file name
  )
  }
```

## Using the function

A function can be used individually

```{r}
run_docs("New_Zealand", "2020-01-01")
```

. . .

And for many (in a loop)

```{r}
purrr::map2(c("New_Zealand", "United_Kingdom"), "2020-01-01", run_docs)
```

## Next Section {.smaller}

Credit: Blog by Meghan Hall, [Tips for Custom Parameterized PDFs in Quarto](https://meghan.rbind.io/blog/quarto-pdfs/#parameterized-reports-in-r-and-quarto)

Read more in the blog from Mike Mahoney, [How to use Quarto for Parametized Reporting](https://www.mm218.dev/posts/2022-08-04-how-to-use-quarto-for-parameterized-reporting/#parameterized-reports) including Parametized SQL
