---
title: "Introduction to Quarto"
title-slide-attributes: 
  data-background-color: "#43464B"
subtitle: "Session - Introduction"
execute: 
  eval: true
---

```{r}
#| label: packages
library(emo)
library(countdown)
```

## Agenda - session one (about 3.5 hours)

Chapter overview

::: {.fragment .fade-in}
- Getting set up 
- What's inside?  
:::
::: {.fragment .fade-in}
--------- Break -----------  
:::
::: {.fragment .fade-in}
- Text 
- Images 
- Code chunks  
:::



## Agenda - session two (about 3.5 hours)

Chapter overview

::: {.fragment .fade-in}
- Inline code 
- Tabs 
:::
::: {.fragment .fade-in}
--------- Break -----------
:::
::: {.fragment .fade-in}
- Output Formats
- Parameters
- Command Line
- Loop reports
- Extras
:::

## Course Aims

::: incremental
-   Get set up using Quarto within RStudio
-   To introduce Quarto as a way to produce reports/slides/books and websites
-   Show the potential for using Quarto as a work flow for any analysis project
:::

## What is Quarto - what do you think?

::: incremental
- "An open-source scientific and technical publishing system"

- A document format (`.qmd`) 

- An R package named `{quarto}`

- A publishing system for making dynamic documents with R, Python, Julia and Observable 

- "a unified authoring framework for data science, combining your code, its results, and your prose"

- Wizardry 
:::

## What is Quarto - answers

::: incremental
- ["An open-source scientific and technical publishing system"](https://quarto.org/) `r emo::ji("heavy_check_mark")`

- A document format (`.qmd`) `r emo::ji("heavy_check_mark")`

- [An R package named `{quarto}`](https://github.com/quarto-dev/quarto-r) `r emo::ji("heavy_check_mark")`

- A publishing system for making dynamic documents with R, Python, Julia and Observable `r emo::ji("heavy_check_mark")`

- ["a unified authoring framework for data science, combining your code, its results, and your prose"](https://r4ds.hadley.nz/quarto.html) `r emo::ji("heavy_check_mark")`

- Wizardry `r emo::ji("wizard")`
:::

# Let's get started

## Checking first...

That everyone is:

* set up on RStudio Cloud (own laptops are fine to use instead with the latest RStudio)

## Also note...

[TODO]
Code doesn't copy to MS Teams with the correct indentations but code can be copied from the [slides](),

:::{.callout-important collapse=false appearance='default' icon=true}
## Quarto the CLI command line interface (important)
- Quarto is an [addition](https://quarto.org/docs/get-started/) to the RStudio IDE
- {quarto} the package has functions the run some of the commands - more later
:::


## Together we'll open a Quarto template

* Go to `File/New File/Quarto document...`
* A wizard will prompt a Title and Author
* **Render** this document and save the file when the wizard appears

:::{.callout-warning collapse=false appearance='default' icon=true}
## File permissions (warning)
- the file must have access to write/save files to the same folder that the `.qmd` is in
- it will run create supporting files and folders and then clear them away
:::

## Your turn

[TODO] Look at the source, then **Render** to HTML

Try to identify these parts in the source and the output:

:::: {.columns}

::: {.column width='40%'}

1. The **metadata**
1. The **text** 
1. The **code**
1. The **output**

**If this was easy**, try to find all code that produces a *plot*.
:::

::: {.column width='60%'}

```{r}
countdown::countdown(minutes = 2,
                     color_border = "#005EB8",
                     color_text = "#005EB8",
                     color_running_text = "white",
                     color_running_background = "#005EB8",
                     color_finished_text = "#005EB8",
                     color_finished_background = "white",
                     margin = "0.9em",
                     font_size = "2em")
```
:::

::::

## Basic anatomy I

[TODO]
We look at the *source* anatomy for `qmd` together:

1. The **metadata**
1. The **text** 
1. The **code**

### Basic anatomy II

1. The **output**

## End session
