---
title: "Tabset panels"
title-slide-attributes: 
  data-background-color: "#43464B"
subtitle: "Session - tabs"
author: "Zoë Turner"
format:
  revealjs:
    theme: [default, nhsr-quarto.scss]
    logo: https://raw.githubusercontent.com/nhs-r-community/assets/main/logo/nhsr-logo.svg
    code-link: true
    css: nhsr-quarto.scss
    self-contained: true
    preview-links: true
execute: 
  echo: false
  eval: false
embed-resources: true  
editor_options: 
  chunk_output_type: inline
---

```{r}
#| label: packages
#| eval: true
#| include: false
library(countdown)
library(knitr)
```

## Breaking up long reports in HTML

::: {.incremental}
- Used to allow users to toggle between sections and breakup very long HTML.
- Cannot be used in reports that are static like Word or pdf.
:::


## Tabsets rely upon on few features

As a reminder, in markdown there is a hierarchy of hashes for tabs

```markdown
# Country analysis
## Overview
## Covid cases
```

. . .

And Quarto specific code is denoted by `:::` at the start and end of code to be affected. 

For example 

```markdown
::: {.panel-tabset}
# Country analysis
## Overview
## Covid cases
:::
```

## Let's try this

First of all we'll install a GitHub package which changes RStudio to have an add in menu:

```{r}
#| echo: true

# install.packages("remotes")  # if not yet installed
remotes::install_github("matt-dray/quartostamp")
```

. . .

Then we'll highlight from `## Overview` to the very end and select `Insert Tabset` from the Addins menu (under Help) and Render

. . .

:::{.callout-important collapse=false appearance='default' icon=true}
## Note the level of headers
- {quartostamp} can be used with or without text
:::

## Styling tabs

It's possible to change the view of the tabs:

```markdown
::: {.panel-tabset .nav-pills}
# Country analysis
## Overview
## Covid cases
:::
```
## Next Section 

