---
title: "Output formats"
subtitle: "Session - Creating things from Quarto"
---

## Wizard

Using the wizard in RStudio gives a selection of output possibilities:

::: {.incremental}
- html (default and very accessible as well as interactive)
- word
- pdf
:::

A full list is on the [Quarto documentation website](https://quarto.org/docs/output-formats/all-formats.html) with links to the code to use in the YAML

## Rendering to multiple outputs

Whilst it's possible to list several outputs in the YAML:

```markdown
format: 
  html:
    toc: true
  docx:
    toc: true
```
only the first will render with the `Render` button in RStudio.

## Using {quarto} package

The {quarto} package (which is different to Quarto which is in RStudio) can render to different formats:

```{r}
#| echo: fenced

quarto::quarto_render(output_format = "docx")
```

. . .

:::{.callout-warning collapse=false appearance='default' icon=true}
## Quarto project
- This function prompts for the project to be a Quarto project
- In RStudio this can be set up from the beginning with `File > New Project... > Quarto project`
- An additional file called `_quarto.yml` is generated with code:
```markdown
project:
  title: "intro-quarto"
```
:::

## And all formats

The following can generate all outputs:

```{r}
#| echo: fenced

quarto::quarto_render(output_format = "all")
```

## Run any file

It's possible to Render any Quarto file (even when not open in RStudio):

```{r}
#| echo: fenced

quarto::quarto_render("images_report/example_report.qmd")
```


## Next Section
