---
title: "Rendering multiple reports"
subtitle: "Session - using Quarto Projects"
---

```{r}
#| label: packages
#| eval: true
#| echo: false
#| include: false
library(quarto)

```

## Rendering as you save

Using the button on the RStudio panel (under the tabs)

Whenever you save this updates the document

:::{.callout-tip collapse=false appearance='default' icon=true}
## Cloud default settings are different!
On a computer the default 

`Global Options.../Code/Saving/Automatically save when editor loses focus`

is not ticked which allows for the `Render on Save` function. On Posit Cloud it _is_ ticked.
:::


## Combining features in RStudio

The settings in the cog (next to `Render`) include:

::: {.incremental}
- `Preview in View Pane` which opens a Viewer pane within RStudio
- `Chunk output` Inline is within the current screen but there is the option to only have output appear in the Console.
:::


## Rendering from the R Console

Using the {quarto} package the following renders *everything* in the project

```{r}
#| echo: fenced
quarto::quarto_render()
```

. . .

:::{.callout-warning collapse=false appearance='default' icon=true}
## Quarto project
- This command will only work if the project is a Quarto Project
- This requires a file called `_quarto.yml` and can start off with just the code:
``` markdown
project:
  title: "intro-quarto"
```
:::

## Rendering from the Terminal

Where the prompt is `$` commands can be used for `git` and also `quarto`:

```markdown
quarto render
```
## Adding more to the `_quarto.yml`

If there are several files using the same YAML information this can be put into the `_quarto.yml` file so it only has to be written once:

```markdown
project:
  title: "intro-quarto"
author: "Zoë Turner"
execute: 
  echo: false
  eval: false
embed-resources: true
```

## Excluding files

The `_quarto.yml` can be used to list specific files to render or, alternatively, have files to exclude:

```markdown
project:
  title: "intro-quarto"
  render: 
    - "*.qmd"
    - "!*.md"
    - "!folder-example/"
```

This includes anything with a `.qmd` ending but not a `.md` and not for files that are in a folder called `files/`

## Next Section 
