---
title: "Tabset panels"
subtitle: "Session - tabs"
editor_options: 
  chunk_output_type: inline
---

```{r}
#| label: packages
#| eval: true
#| include: false
library(countdown)
library(knitr)
```

## Breaking up long reports in HTML

::: {.incremental}
- Allows users to toggle between sections and breakup very long HTML
- Cannot be used in reports that are static like Word or pdf
:::


## Tabsets rely upon on few features

As a reminder, in markdown there is a hierarchy of hashes for tabs

```markdown
# Country analysis
## Overview
## Covid cases
```

. . .

And Quarto specific code is denoted by `:::` at the start and end of code to be affected. 

For example 

```markdown
# Country analysis
::: {.panel-tabset}
## Overview
## Covid cases
:::
```

## Let's try this

First of all we'll install a GitHub package which changes RStudio to have an add in menu:

```{r}
#| echo: true

# install.packages("remotes")  # if not yet installed
remotes::install_github("matt-dray/quartostamp")
```

. . .

Then we'll `Insert Tabset` from the Addins menu (under Help) and then copy the header code over the `Tab A` and `Tab B`

## Styling tabs

It's possible to change the view of the tabs by adding `.nav-pills`:

. . .

```markdown
# Country analysis
::: {.panel-tabset .nav-pills}
## Overview
## Covid cases
:::
```
## Next Section 

